---
title: "README"
author: "Chase Clark"
date: "January 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This app takes the responses from a Google Forms survey and correlates to members attending a Meetup.com Meetup


Skills: 
- Shiny
- Reading from API
  - Google Sheets ApI 
  - Meetup API
- Parsing data tables and json structures 
- Organizing results via Shiny HTML tags (tables)
- Simple base R plot
- Reactive UI elements (reactive slider bars)


Challenges:

- Can you add a button that will shuffle groups?
- Can you add a skill-summary graph under each group column?
- Can you use clustering of skill levels to make the groups instead of simple cutoffs?





Note: For privacy I have generated a table of random names with a variety of skill levels. I will also explain the meetup API
I used but will remove the actual API I used for anonymity of CRUG participants.



```{r}
library(tidyverse)
library(googlesheets)
library(randomNames)
library(magrittr)

set.seed(42)
# Generate random names
firstNames  <- randomNames::randomNames(75, which.names = "first")
lastNames   <- randomNames::randomNames(75, which.names = "last")

# Create Tibble
responses <- bind_cols(a=firstNames,b=lastNames)

# Recapitulate some columns that represent questions in the Google Forms survey
responses %<>% mutate("What is your name? (First and Last)"=paste(a,b)) %>%  dplyr::select(`What is your name? (First and Last)`)


# Make some artificial data with easy clusters

set.seed(1)
    a<-sample(seq(from = 1, to = 3, by = 1), size = 25, replace = TRUE)
    b<-sample(seq(from = 4, to = 6, by = 1), size = 25, replace = TRUE)
    c<-sample(seq(from = 7, to = 10, by = 1), size = 25, replace = TRUE)
z1<-(c(a,b,c))
set.seed(10)
    a<-sample(seq(from = 1, to = 3, by = 1), size = 25, replace = TRUE)
    b<-sample(seq(from = 4, to = 6, by = 1), size = 25, replace = TRUE)
    c<-sample(seq(from = 7, to = 10, by = 1), size = 25, replace = TRUE)
z2<-(c(a,b,c))


responses %<>% mutate("Experience with R"= z1)
responses %<>% mutate("Experience with Shiny"= z2)








saveRDS(responses, "responses.RDS")

# For info on how to pull using the googlesheets API, please see Jenny Brian's GitHub
# https://github.com/jennybc/googlesheets
        # surveyResponses <- gs_key(" Insert Key Here ")
        #      surveyResponses %>%  gs_read(ws = "Form Responses 1")



```





